Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-25 MS_thesis.tex
Move acknowledgement of KVPY and PARAM into a separate section

%The acknowledgements go here.
\acknowledgments{
\vspace{-0.1cm}
First and foremost, I am grateful to my advisors, Prof. Vishwesha Guttal and Prof. Rohini Balakrishnan, for their masterful mentoring. The enormous academic freedom they gave me to pursue essentially whichever ideas seemed promising at the time, coupled with their readiness to provide detailed guidance whenever I asked for it, made working with them an incredibly enriching experience. Their constant focus on the bigger picture was vital to helping me see the forest when I was stuck looking at the trees. Both Vishu and Rohini are brilliant scientists and fantastic mentors, and their mentorship and guidance have deeply impacted my ways of thinking about science and mentoring. I am also grateful to all the members of the \href{https://teelabiisc.wordpress.com/}{Theoretical Ecology and Evolution lab} and the \href{https://sites.google.com/view/rohinibalakrishnanlab/home}{Animal Communication and Bioacoustics Lab} for providing a supportive and productive working environment.

@@

Finally, I am eternally indebted to my parents, Raja and Vidya. They have unfailingly supported me at every step of my life, and have nurtured and encouraged an inquisitive wonder of the world that no doubt played a vital role in helping me choose this career path. Not many parents would raise their children on Durrell and Feynman or take time out of their day to help their child find the right plant or jar for keeping an insect in the house. Upon finding out that their child has an early fascination with praying mantids and finding that there is no accessible information about the topic, not many parents would encourage their child to try and write their own source on the subject by keeping these insects at home and documenting their behavior. Upon finding out that their child was interested in snakes, not many parents would encourage this interest and actively accompany them to animal rescue centers, snake parks, and herpetology summer camps. Not many parents would be okay with their child spending weeks in the rainforest with no cellular network catching snakes and looking for frogs in the dark with a flashlight. Certainly, not many Indian parents would let their child pursue this love of animals professionally and allow them to virtually ignore the more `mainstream' entrance exams for engineering and medical colleges in favor of fully committing to the pipe dream of getting accepted by an IISER or IISc. Not many parents would provide an actively supporting environment at home for an MS project, without questioning their child's future plans or PhD application process at any stage, and just trusting that the child will figure things out. Not many parents would provide fantastic support during difficult emotional situations or not blink an eye when their child decides to grow their hair out or get a tattoo. Thank you for always believing in me and letting me make my own choices, both small and large.
}
\allowdisplaybreaks %allow align envts to go across pages

>>>>

%The acknowledgements go here.
\acknowledgments{
First and foremost, I am grateful to my advisors, Prof. Vishwesha Guttal and Prof. Rohini Balakrishnan, for their masterful mentoring. The enormous academic freedom they gave me to pursue essentially whichever ideas seemed promising at the time, coupled with their readiness to provide detailed guidance whenever I asked for it, made working with them an incredibly enriching experience. Their constant focus on the bigger picture was vital to helping me see the forest when I was stuck looking at the trees. Both Vishu and Rohini are brilliant scientists and fantastic mentors, and their mentorship and guidance have deeply impacted my ways of thinking about science and mentoring. I am also grateful to all the members of the \href{https://teelabiisc.wordpress.com/}{Theoretical Ecology and Evolution lab} and the \href{https://sites.google.com/view/rohinibalakrishnanlab/home}{Animal Communication and Bioacoustics Lab} for providing a supportive and productive working environment.

@@

Finally, I am eternally indebted to my parents, Raja and Vidya. They have unfailingly supported me at every step of my life, and have nurtured and encouraged an inquisitive wonder of the world that no doubt played a vital role in helping me choose this career path. Not many parents would raise their children on Durrell and Feynman or take time out of their day to help their child find the right plant or jar for keeping an insect in the house. Upon finding out that their child has an early fascination with praying mantids and finding that there is no accessible information about the topic, not many parents would encourage their child to try and write their own source on the subject by keeping these insects at home and documenting their behavior. Upon finding out that their child was interested in snakes, not many parents would encourage this interest and actively accompany them to animal rescue centers, snake parks, and herpetology summer camps. Not many parents would be okay with their child spending weeks in the rainforest with no cellular network catching snakes and looking for frogs in the dark with a flashlight. Certainly, not many Indian parents would let their child pursue this love of animals professionally and allow them to virtually ignore the more `mainstream' entrance exams for engineering and medical colleges in favor of fully committing to the pipe dream of getting accepted by an IISER or IISc. Not many parents would provide an actively supporting environment at home for an MS project, without questioning their child's future plans or PhD application process at any stage, and just trusting that the child will figure things out. Not many parents would provide fantastic support during difficult emotional situations or not blink an eye when their child decides to grow their hair out or get a tattoo. Thank you for always believing in me and letting me make my own choices, both small and large. I love you.
}

\funding{
I am a recipient (Registration no. SX-1711025) of the Kishore Vaigyanik Protsahan Yojana (KVPY) fellowship from the Department of Science and Technology, Government of India, and gratefully acknowledge the same for providing financial support.

The support and the resources provided by the PARAM Brahma Facility under the National
Supercomputing Mission, Government of India at the Indian Institute of Science Education
and Research (IISER), Pune are gratefully acknowledged; However, it is worth explicitly noting that while I did briefly run some scripts on the PARAM-Brahma facility that were related to my thesis project, none of the scripts or simulations run on the PARAM-Brahma supercomputer ultimately contributed in any way, shape, or form to any material presented in this thesis --- The main text is completely analytical, and Appendix \ref{App_examples} only uses very simple simulations that were run on my personal laptop; The particular simulations I ran on PARAM also did not help me gain any insight or understanding towards any of the phenomena and/or models studied in this thesis.
}

\allowdisplaybreaks %allow align envts to go across pages
